---
title: "Metadata Creation with dataspice"
author: "Natalie Elliot"
---

## Step 2: Quarto File in New R Project for Versioning

This .qmd file contains the steps and chunk code in R syntax necessary for completing Activity 3.

## Step 3.1: Install dataspice package

```{r install dataspice package, echo=TRUE}
install.packages("dataspice")
```

## Step 3.2: Initialize the Metadata Structure

```{r load dataspice and create metadata templates, echo=TRUE}
library(dataspice)
create_spice(dir = "data")
```

## Step 4.1: Populating Metadata Files

### Editing creators.csv

```{r editing creators, echo=TRUE}
edit_creators()
readr::read_csv('data/metadata/creators.csv')
```

### Preparing access.csv

```{r preparing access, echo=TRUE}
prep_access()
edit_access()
readr::read_csv('data/metadata/access.csv')
```

### Editing biblio.csv

```{r editing biblio, echo=TRUE}
edit_biblio()
readr::read_csv('data/metadata/biblio.csv')
```

### Editing attributes.csv

```{r editing attributes, echo=TRUE}
prep_attributes()
edit_attributes()
readr::read_csv('data/metadata/attributes.csv')
```

## Step 4.2: Create JSON-LD Metadata File

```{r compile as structured json file, echo=TRUE}
write_spice()
```

### Install and load packages for viewing JSON-LD Metadata file

```{r install and load json related packages for viewing, echo=TRUE}
install.packages("listviewer") # I already have jsonlite package installed
jsonlite::read_json(here::here("data", "metadata", "dataspice.json")) %>% 
    listviewer::jsonedit()
```

## Step 4.3: Build README site

```{r build readme site, echo=TRUE}
build_site()
```
